Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2024-09-16 Latex_files/Thesis/chapters/chapter 1/main.tex

\subsection{Two Step Nucleation}
The two step nucleation theory is an extension to the CNT, colloid simulations 
showed that short range (such as in proteins \cite{Wolde1997, Gliko2005}) 
interactions allow for the formation of a liquid-liquid metastable phase from 
which a new solid phase could form \cite{Anderson2002, Karthika2016}. 
\textit{in situ} techniques for studying nucleation several papers reported 
the presence of stable liquid-like clusters that formed prior to nucleation
\cite{Savage2009, Wolde1997, Soga1999}. It can be understood by Oswald's rule
\cite{Ostwald1897}, which says that any crystallising system does not immediately 
take the path to the lowest possible energy state but instead first transitions 
to the state with the smallest free energy barrier, further transitions can still 
occur but this pathway minimises the overall free energy cost. If we consider 
the free energy diagram from before (fig.~\ref{fig:free_energy}) we can consider 
a case where the supersaturation is low ($S\approx1.01$) then a dense liquid 
droplet will have a lower chemical potential than the surrounding fluid but 
the crystalline phase will have a subsequently lower chemical potential than 
the dense liquid phase. Initially it was suspected that the formation of the 
dense liquid phase was a result of stochastic density fluctuations in the system; 
further simulations suggest that the the local bond order is a stronger driving 
force than the local density \cite{Tan2013}.

>>>>

\subsection{Two Step Nucleation}
The two step nucleation theory is an extension to the CNT that suggests 
that prior to nucleation, the solute will cluster together. This was 
shown via colloid simulations showed that short range (such as in proteins \cite{Wolde1997, Gliko2005}) interactions allow for the formation of a liquid-liquid metastable phase from which a new solid phase could form \cite{Anderson2002, Karthika2016}. Several papers later reported the 
presence of stable liquid-like clusters that formed prior to nucleation \cite{Savage2009, Wolde1997, Soga1999}. The formation of these clusters 
can be understood by Oswald's rule; which says that any crystallising 
system does not immediately take the path to the lowest possible energy 
state but instead first transitions to the state with the smallest free 
energy barrier \cite{Ostwald1897}. Further phase transitions can still 
occur but this pathway minimises the overall free energy cost. Initially 
it was suspected that the formation of the dense liquid phase was a 
result of stochastic density fluctuations in the system. However, 
simulations suggest that the the local bond order is a stronger driving 
force than the local density \cite{Tan2013}. Studies into two step 
nucleation in Glycine solutions have noted that the solutions need to be 
aged before the presence of clusters was detected. This suggests that 
there exist further barriers to the formation of clusters in some systems,
this has lead to instead calling this phenomena as Multi-step Nucleation.

\subsection{Non-classical Nucleation}

### 2024-09-16 Latex_files/Thesis/chapters/chapter 2/main.tex

Where $k$ is the wave number of the electromagnetic radiation 
($k = 2\pi/\lambda$). This combined with the constraints of 
Maxwell's equations leaves very few exact solutions apart from 
spherical or planar waves, both of which can be converted between 
with relative ease. For example, a plane wave electric field can 
be expanded into spherical harmonics and likewise any spherical 
wave can be described as a combination of plane waves offset from 
one another. For a single plane wave the incident, internal, and 
scattered fields are given as: 
\begin{align}
	\label{eq:incident}
	{\bf E}_{\rm inc}({\bf r})
	&=
    E_0 \sum_{nm}^\infty \left[
    a_{nm}{\bf M}_{nm}^{(1)}({\bf r})
    + b_{nm}{\bf N}_{nm}^{(1)}({\bf r})\right]
  \\
  \label{eq:internal}
  {\bf E}_{\rm int}({\bf r})
  &=
    E_0 \sum_{n=1}^\infty i^n\frac{2n+1}{n(n+1)}\left[
    -id_{nm}{\bf N}_{nm}^{(1)}({\bf r}) + c_{nm}{\bf M}_{nm}^{(1)}({\bf r})
    \right]
  \\
  \label{eq:scattered}
  {\bf E}_{\rm scat}({\bf r})
  &=
    E_0 \sum_{n=1}^\infty  i^n\frac{2n+1}{n(n+1)}\left[
      -i p_{nm}{\bf N}_{nm}^{(3)}({\bf r})+q_{nm}{\bf M}_{nm}^{(3)}({\bf r})
    \right] 
    \\
	\mathbf{E}_{tot}({\bf r}) &= 
	\begin{cases}
		{\bf E}_{\rm inc}({\bf r}) + {\bf E}_{\rm scat}({\bf r}) & \text{if \textbf{r} outside}
		\\ 
		{\bf E}_{\rm int}({\bf r}) & \text{if \textbf{r} inside}
	\end{cases}
\end{align}

where $a_{nm}$, $b_{nm}$, $c_{nm}$, $d_{nm}$, $p_{nm}$, and $q_{nm}$
are the expansion coefficients of each of the fields, and $M^{(1)}_{nm}$ 
and $N^{(1)}_{nm}$ are the vector spherical harmonics. For the incident
field computing its expansion coefficients is possible via analytical
methods and are completely dependent on the beam conditions imposed by
the user. However, computing the expansion coefficients of the
internal and scattered fields is far more tedious depending on the
shape of the target and what properties of the scattered field are
desired --- see sec.~\ref{sec:scattering}.  From an optical
trapping perspective the force exerted by a focused electric field can
be found by computing the Maxwell stress tensor which only requires
the total magnitude of the incident and scattered fields. An alternative
method is to compute the momentum carried by the incident and scattered
beams and taking the difference between to measure the momentum 
transferred to the particle. This project utilises the results from 
Farsund \cite{Farsund1996} but in the form used by Crichton 
\cite{Crichton2000THEMD}. As an example the linear momentum carried 
by any beam can be computed via:
\begin{equation}
	\label{eq:linear_momentum_in}
	\begin{split}
		\langle P_{z,\ in} \rangle
		&=
		-\frac{1}{4\pi k^2}\sum_{n,m} \left(\frac{m}{n(n+1)}\Im[a_{nm}b^*_{nm}] \right.
		\\ 
		&+\frac{1}{n+1}\left[\frac{n(n+2)(n-m+1)(n+m+1)}{(2n+1)(2n+3)} \right]^{1/2}
		\\
		& \left.\times\Im[b_{nm}b^*_{nm}+a_{nm}a^*_{n+1m}] \right)
	\end{split}
\end{equation}

@@

Using a  MATLAB package called \textit{Optical Tweezer Toolbox} 
or \textit{ott} \cite{Nieminen2007} we can compute the beam 
shape coefficients ($a_{nm}$ \& $b_{nm}$) for any desired beam 
type. Using the results from \cite{Farsund1996} we can then 
compute both the optical force and torque using the beam 
coefficients and the scattering coefficients ($q_{nm}$ \& $p_{nm}$) 
which are found by calculating the dimer's $T$-matrix via \textit{mstm} \cite{Mackowski2011} and then using \eqref{eq:t_matrix}. The 
total force in along the z-direction and the total torque about 
the z-axis are provided
\begin{equation}
	\label{eq:optical_force}
\begin{split}
  \bold{F_z}
  &=
    -\frac{1}{4\pi k^2}\sum_{n,m} \left(\frac{m}{n(n+1)}\Im[a_{nm}b^*_{nm}-p_{nm}q^*_{nm}] \right.
  \\ 
  &+\frac{1}{n+1}\left[\frac{n(n+2)(n-m+1)(n+m+1)}{(2n+1)(2n+3)} \right]^{1/2}
  \\
  & \left.\times\Im[b_{nm}b^*_{nm}+a_{nm}a^*_{n+1m}-q_{nm}q^*_{nm}+p_{nm}p^*_{n+1m}] \right)
\end{split}
\end{equation}
\begin{equation}
\begin{split}
  \bold{T_z}
  &=
    -\frac{1}{8\pi k^3}\sum_{n,m} \left(\frac{m}{n(n+1)}[|a_{nm}|^2+|b_{nm}|^2-|p_{nm}|^2-|q_{nm}|^2] \right.
  \\ 
  &+\frac{2}{n+1}\left[\frac{n(n+2)(n-m+1)(n+m+1)}{(2n+1)(2n+3)} \right]^{1/2}
  \\
  & \left.\times\Re[b_{nm}a^*_{nm}+a_{nm}b^*_{n+1m}-p_{nm}q^*_{nm}+q_{nm}p^*_{n+1m}] \right)
\end{split}
\end{equation}

@@

The incident beam is simple enough to define given our set up parameters, 
for the sake of simplicity we assume that our beam is a Laguerre-Gaussian 
beam of mode $[0.0, 0.0]$ (which is simply a pure Gaussian beam). 
\textit{Ott} uses a point matching approach to approximate the beam shape 
coefficients of the incident field by fitting it to the far field estimate, 
the beam is of the form:
\begin{align}
	E_{\rm inc}(r)=\sum^\infty_n\sum^n_{m=-n}a_{mn}RgM_{nm}(r)+b_{nm}RgN_{nm}(r)
\end{align}

where $RgM_{nm}(kr)$ \& $RgN_{nm}(kr)$ are regular vector spherical 
wave functions, these differ from \eqref{eq:incident} and 
\eqref{eq:scattered} in the fact that the field can either be 
expressed as an incoming/outgoing wave (with a 
singularity at the origin) or as a regular wave around the origin; for 
incoming/outgoing waves the wave functions use the first/second forms of 
the Hankel function respectfully. In order to compute the regular spherical 
wave at the origin we replace the Hankel function with the Bessel function 
which is simply the average of the first and second forms of the Hankel 
function, so at the origin we avoid a singularity of the EM field.

We can if we want further restrict the incident beam by setting 
the truncation angle to match our microscope object, this applies a 
hard cut off to the incident beam to better represent experimental 
conditions. In order to compute the scattering from 
the target particle \textit{ott} uses the $T$-matrix method, this is not 
essential for a simple sphere but is essential for complex shaped particles 
such as dimers. The matrix from mstm needs to be repackaged to work with the
\textit{ott} software, converting it from a column vector into a system of 
sub matrices.

>>>>

Where $k$ is the wave number of the electromagnetic radiation 
($k = 2\pi/\lambda$). This combined with the constraints of 
Maxwell's equations leaves very few exact solutions apart from 
spherical or planar waves, both of which can be converted between 
with relative ease. For example, a plane wave electric field can 
be expanded into spherical harmonics and likewise any spherical 
wave can be described as a combination of plane waves offset from 
one another. For a single plane wave the incident, internal, and 
scattered fields are given as: 
\begin{align}
	\label{eq:incident}
	{\bf E}_{\rm inc}({\bf r})
	&=
    E_0 \sum_{nm}^\infty \left[
    a_{nm}{\bf M}_{nm}^{(1)}({\bf r})
    + b_{nm}{\bf N}_{nm}^{(1)}({\bf r})\right]
  \\
  \label{eq:internal}
  {\bf E}_{\rm int}({\bf r})
  &=
    E_0 \sum_{n=1}^\infty i^n\frac{2n+1}{n(n+1)}\left[
    -id_{nm}{\bf N}_{nm}^{(1)}({\bf r}) + c_{nm}{\bf M}_{nm}^{(1)}({\bf r})
    \right]
  \\
  \label{eq:scattered}
  {\bf E}_{\rm scat}({\bf r})
  &=
    E_0 \sum_{n=1}^\infty  i^n\frac{2n+1}{n(n+1)}\left[
      -i p_{nm}{\bf N}_{nm}^{(2)}({\bf r})+q_{nm}{\bf M}_{nm}^{(2)}({\bf r})
    \right] 
    \\
	\mathbf{E}_{tot}({\bf r}) &= 
	\begin{cases}
		{\bf E}_{\rm inc}({\bf r}) + {\bf E}_{\rm scat}({\bf r}) & \text{if \textbf{r} outside}
		\\ 
		{\bf E}_{\rm int}({\bf r}) & \text{if \textbf{r} inside}
	\end{cases}
\end{align}

where $a_{nm}$, $b_{nm}$, $c_{nm}$, $d_{nm}$, $p_{nm}$, and $q_{nm}$
are the expansion coefficients of each of the fields, and $M_{nm}$ 
and $N_{nm}$ are the vector spherical harmonics. The superscripts
denote whether the field is inward or outward propagating; so a 
superscript (1) is inward propagating, and (2) is outward propagating.  
For the incident field computing its expansion coefficients is possible 
via analytical methods and are completely dependent on the beam 
conditions imposed by the user. However, computing the expansion 
coefficients of the internal and scattered fields is far more 
tedious depending on the shape of the target and what properties 
of the scattered field are desired --- see sec.~\ref{sec:scattering}.  
From an optical trapping perspective the force exerted by a focused 
electric field can be found by computing the Maxwell stress tensor 
which only requires the total magnitude of the incident and scattered 
fields. An alternative method is to compute the momentum carried by 
the incident and scattered beams and taking the difference between 
to measure the momentum transferred to the particle. This project 
utilises the results from Farsund \cite{Farsund1996} but in the 
form used by Crichton \cite{Crichton2000THEMD}. As an example the 
linear momentum carried by any beam can be computed via:
\begin{equation}
	\label{eq:linear_momentum_in}
	\begin{split}
		\langle P_{z,\ in} \rangle
		&=
		-\frac{1}{4\pi k^2}\sum_{n,m} \left(\frac{m}{n(n+1)}\Im[a_{nm}b^*_{nm}] \right.
		\\ 
		&+\frac{1}{n+1}\left[\frac{n(n+2)(n-m+1)(n+m+1)}{(2n+1)(2n+3)} \right]^{1/2}
		\\
		& \left.\times\Im[b_{nm}b^*_{nm}+a_{nm}a^*_{n+1m}] \right)
	\end{split}
\end{equation}

@@

Using a  MATLAB package called \textit{Optical Tweezer Toolbox} 
or \textit{ott} \cite{Nieminen2007} we can compute the beam 
shape coefficients ($a_{nm}$ \& $b_{nm}$) for any desired beam 
type. Using the results from \cite{Farsund1996} we can then 
compute both the optical force and torque using the beam 
coefficients and the scattering coefficients ($q_{nm}$ \& $p_{nm}$) 
which are found by calculating the dimer's $T$-matrix via \textit{mstm} \cite{Mackowski2011} and then using \eqref{eq:t_matrix}. The 
total force in along the z-direction and the total torque about 
the z-axis are provided:
\begin{equation}
	\label{eq:optical_force}
\begin{split}
  \bold{F_z}
  &=
    -\frac{1}{4\pi k^2}\sum_{n,m} \left(\frac{m}{n(n+1)}\Im[a_{nm}b^*_{nm}-p_{nm}q^*_{nm}] \right.
  \\ 
  &+\frac{1}{n+1}\left[\frac{n(n+2)(n-m+1)(n+m+1)}{(2n+1)(2n+3)} \right]^{1/2}
  \\
  & \left.\times\Im[b_{nm}b^*_{nm}+a_{nm}a^*_{n+1m}-q_{nm}q^*_{nm}+p_{nm}p^*_{n+1m}] \right)
\end{split}
\end{equation}
\begin{equation}
\begin{split}
  \bold{T_z}
  &=
    -\frac{1}{8\pi k^3}\sum_{n,m} \left(\frac{m}{n(n+1)}[|a_{nm}|^2+|b_{nm}|^2-|p_{nm}|^2-|q_{nm}|^2] \right.
  \\ 
  &+\frac{2}{n+1}\left[\frac{n(n+2)(n-m+1)(n+m+1)}{(2n+1)(2n+3)} \right]^{1/2}
  \\
  & \left.\times\Re[b_{nm}a^*_{nm}+a_{nm}b^*_{n+1m}-p_{nm}q^*_{nm}+q_{nm}p^*_{n+1m}] \right)
\end{split}
\end{equation}

@@

The incident beam is simple enough to define given our set up parameters, 
for the sake of simplicity we assume that our beam is a Laguerre-Gaussian 
beam of mode $[0.0, 0.0]$ (which is simply a pure Gaussian beam). 
\textit{Ott} uses a point matching approach to approximate the beam shape 
coefficients of the incident field by fitting it to the far field estimate. 
From the QPD's perspective it is receiving light both from the incident 
and scattered beam simultaneously, as such both fields must be expressed
using outgoing vector spherical harmonics.
\begin{align}
	E_{\rm inc}(r)&=
	E_0\sum^\infty_{nm}\left[a_{mn}{\bf M}^{(2)}_{nm}({\bf r})+
	b_{nm}{\bf N}^{(2)}_{nm}({\bf r}) \right] 
	\\
	E_{\rm scat}(r)&=E_0 \sum_{n=1}^\infty i^n\frac{2n+1}{n(n+1)}\left[
	-i p_{nm}{\bf N}_{nm}^{(2)}({\bf r})+q_{nm}{\bf M}_{nm}^{(2)}({\bf r})
	\right] 
\end{align}

We can, if we want, further restrict the incident beam by setting 
the truncation angle to match our microscope object, this applies a 
hard cut off to the incident beam to better represent experimental 
conditions. In order to compute the scattering from 
the target particle \textit{ott} uses the $T$-matrix method, this is 
not essential for a simple sphere but is essential for complex shaped 
particles such as dimers. The matrix from mstm needs to be repackaged 
to work with the \textit{ott} software, converting it from a column 
vector into a system of sub matrices.

### 2024-09-16 Latex_files/Thesis/chapters/chapter 4/main.tex

\chapter{Complex Langevin dynamics of spherical dimers}
\label{chapter:langevin_dynamics}
Much of the calibration theory discussed in Chapter 2 assumes that the
target particle in question is a single sphere, one who's scattering and 
motion is easily computed. However, while working with dense colloidal 
suspensions, one often ends up trapping more than one sphere. Li and 
Arlt \cite{Li2008} studied the case of two microspheres trapped in a single 
OT and found that multiple trapped beads could be mistaken for a single 
trapped bead with altered trap stiffness. Theoretical studies on the case 
of two trapped microspheres by Xu~\textit{et~al.} \cite{Xu2005} employed a 
ray-optics based model to show that the two trapped beads are brought into 
physical contact with each other by optical forces and they also calculated 
the axial equilibrium positions of the two trapped beads as a function of 
their size. Experiments in \cite{Praveen2016} confirmed that the two trapped 
beads indeed experience different trap stiffnesses in the vicinity of the 
same potential well. There are further discussions looking into the dynamics 
of a whole host of asymmetrically shaped particles \cite{Loudet2014, ShengHua2005, 
Chetana2022}, their results all showing that predicting the behaviour an 
arbitrary shaped particle comes with great difficulty due to the fact that 
the optical force is dependent on a greater number of variables such as 
orientation and size factors.

With the initial goal of the PhD being to induce nucleation events via a 
spherical micro-rotor the goal of this chapter is to - in a limited capacity
simulate and investigate the influence of a second particle being bound to our 
target sphere. The choice of a dimer, instead of an amorphous solid that 
might better represent a growing crystalline solid, allows us to consider 
how the dynamics of the aggregate change by varying the size factor. 
Additionally, attempting to simulate an amorphous aggregate is rather difficult 
as calculating the optical force and torque is computationally slow. We build 
upon the works of Vigilante \textit{et al} \cite{Vigilante2020} to consider 
asymmetric dimers and how varying size parameters alters the dynamics and 
additionally makes characterising their interactions within an optical trap 
more cumbersome.

In this chapter we will consider how the addition of a second sphere changes 
the trapping dynamics by introducing multiple equilibrium positions. These 
positions are dependent on both the size ratio of the dimer and its orientation
relative to the trap. This is important to address, for while the the dimers' 
diffusive behaviour is the same, regardless of position and orientation, how it
interacts with the trap may produce the wildly different results. Furthermore,
we look at how our dimers interact with circularly polarised light, this is 
especially pertinent as the original plan was to utilise circularly polarised 
light to generate fluid flow in a supersaturated solution. The rotational motion 
of dimers in circularly polarised light goes against much of the established 
literature and suggests that the transfer of spin angular momentum is enabled 
by combining spheres together. And lastly, we demonstrate how a quadrant photo 
diode, performs in characterising the actual interactions between a dimer and 
the optical trap. We do so to demonstrate that much of the dimer's trajectory
information is either lost or poorly described by simple calibration techniques, 
making their motion difficult to characterise.

\subsection{Simulation Parameters}
As a paradigmatic example, consider a dimer suspended in water ($n_p = 1.59, 
n_m = 1.33$) located at the focus of a Gaussian beam (more specifically a 
Laguerre-Gaussian beam of mode $[0,0]$), the beam is focused by a objective 
with numerical aperture of 1.2 and is x polarised. The size ratio of the two 
sphere's is given by $a_{I}/a_{II} = 2$ where $a_{I}$ is kept at $1\ \mu m$ 
unless specified otherwise; the dimer's orientation is given by a unit vector 
connecting the centres of both spheres (see \ref{sec:sim_parameters}). We 
define the 'standard' orientation as being aligned with the direction of 
beam propagation direction - and therefore the 'inverted' orientation is 
defined when the dimer is orientated against the direction of beam 
orientation (see left hand side of figure~\ref{fig:paradigmatic}).

@@

Because the scattering force is only significant in the direction of beam 
propagation the potential well in the transverse plane can still be assumed 
to be harmonic around the central beam axis. The axial optical force cannot 
be assumed to behave as a simple harmonic trap. The methodology for computing 
optical forces has been covered extensively for a number of different trapping 
conditions \cite{RanhaNeves2019}, so it is relatively easy to compute the 
trapping force and determine where a simple sphere would be located relative 
to focal point of the laser by finding the position that minimises the net 
optical force in a negative feed back loop ($\delta F/\delta x < 0$) - we can 
assume that for a dielectric sphere the optical torque is negligible. For a 
dimer (or any arbitrary spherical aggregate), we now must consider both its 
position and orientation and find where the net optical force and torque are 
minimised.

>>>>

\chapter{Complex Langevin dynamics of spherical dimers}
\label{chapter:langevin_dynamics}
Much of the calibration theory discussed in Chapter 2 assumes that the
target particle in question is a single sphere, one whose scattering and 
motion is easily computed. However, while working with dense colloidal 
suspensions, one often ends up trapping more than one sphere. Li and 
Arlt \cite{Li2008} studied the case of two microspheres trapped in a single 
OT and found that multiple trapped beads could be mistaken for a single 
trapped bead with altered trap stiffness (see \ref{sec:harmonic_traps}). Theoretical studies on the case of two trapped microspheres by Xu~\textit{et~al.} \cite{Xu2005} employed a ray-optics based model to show 
that the two trapped beads are brought into physical contact with each 
other by optical forces and they also calculated the axial equilibrium positions of the two trapped beads as a function of their size. Experiments 
in \cite{Praveen2016} confirmed that the two trapped beads indeed experience different trap stiffnesses in the vicinity of the same potential well.

There are further discussions looking into the dynamics 
of a whole host of asymmetrically shaped particles \cite{Loudet2014, ShengHua2005, Chetana2022}, their results all showing that predicting the behaviour an arbitrary shaped particle comes with great difficulty due to 
the fact that the optical force is dependent on a greater number of variables such as orientation and size factors.

With the initial goal of the PhD being to induce nucleation events via a 
spherical micro-rotor, the aim of this chapter is to - in a limited capacity
simulate and investigate the influence of a second particle being bound to our 
target sphere. The choice of a dimer, instead of an amorphous solid that 
might better represent a growing crystalline solid, allows us to consider 
how the dynamics of the aggregate change by varying the size factor. 
Additionally, attempting to simulate an amorphous aggregate is rather difficult 
as calculating the optical force and torque is computationally slow. We build 
upon the works of Vigilante \textit{et al} \cite{Vigilante2020} to consider 
asymmetric spherical dimers and how varying size parameters alters the 
dynamics and additionally makes characterising their interactions within an optical trap more cumbersome.

In this chapter we will consider how the addition of a second sphere 
changes the trapping dynamics by introducing multiple equilibrium 
positions. These positions are dependent on both the size ratio of 
the dimer and its orientation relative to the trap. This is important 
to address, for while the the dimers' diffusive behaviour is the same, regardless of position and orientation, how it interacts with the trap 
may produce the wildly different results. Furthermore, we look at how 
our dimers interact with circularly polarised light, this is especially pertinent as the original plan was to utilise circularly polarised 
light to generate fluid flow in a supersaturated solution. The rotational motion of dimers in circularly polarised light goes against much of the established literature and suggests that the transfer of spin angular 
momentum is enabled by combining particles together. And lastly, we 
demonstrate how a quadrant photo diode, performs in characterising 
the actual interactions between a dimer and the optical trap. We do so 
to demonstrate that much of the dimer's trajectory information is 
either lost or poorly described by simple calibration techniques, 
making their motion difficult to characterise.

\subsection{Simulation Parameters}
As a paradigmatic example, consider a dimer suspended in water 
($n_p = 1.59, n_m = 1.33$) located at the focus of a Gaussian 
beam (more specifically a Laguerre-Gaussian beam of mode $[0,0]$, 
see \eqref{eq:incident}), the beam is focused by a objective with 
numerical aperture of 1.2 and is x polarised. The size ratio of 
the two spheres is given by $a_{I}/a_{II} = 2$ where $a_{I}$ is 
kept at $1\ \mu m$ unless specified otherwise; the dimer's 
orientation is given by a unit vector connecting the centres of 
both spheres (see \ref{sec:sim_parameters}). We define the 
'standard' orientation as being aligned with the direction of beam 
propagation direction - and therefore the 'inverted' orientation is 
defined when the dimer is orientated against the direction of beam 
orientation (see left hand side of figure~\ref{fig:paradigmatic}).

@@

Because the scattering force is only significant in the direction of 
beam propagation \cite{Capitanio2002} we can assume there is only a 
single potential well in the transverse plane. Along the beam axis, 
such an assumption is no longer valid due to fact that spherical 
aggregates experience inter-particle scattering. This is a key reason
for using \textit{mstm} as it accounts for that behaviour. The 
methodology for computing optical forces has been covered extensively 
for a number of different trapping conditions \cite{RanhaNeves2019}. 
So it is relatively easy to compute the trapping force and determine 
the equilibrium position by finding the position that minimises the 
net optical force and the local gradient is negative ($\delta F/
\delta x < 0$) - we can assume that for a dielectric sphere the 
optical torque is negligible. For a dimer (or any arbitrary spherical aggregate), we now must consider both its position and orientation 
and find where the net optical force and torque are minimised.

### 2024-09-16 Latex_files/Thesis/chapters/chapter 5/main.tex

\section{Monitoring Stochastic rotational motion using static light scattering}
Part of the optical fibre arrangement borrows code from the 
optical tweezer simulations discussed in Chapter 2 and 4. 
Rather than repeat the simulation details we will instead 
only focus on the specifics of 
\subsection{Coordinate System}
In the case of our probe beam the +z direction points from the surface of the 
probe directly to the centre of diffusion in our dimer, with the +y direction 
pointing towards what would be our trapping beam, and the +x direction pointing 
into the page. The origin of our coordinate system is fixed on the centre of 
the focus of our trapping beam, meaning as our dimer's centre of diffusion moves 
the origin is kept constant.

\subsection{Beam}
The probe is a defined as a plane wave by setting the Gaussian beam parameter 
$C_B$ to 0. We also say the beam is un-polarized by defining the Stokes vector 
as $[1,0,0,0]$. The plane wave in \textit{mstm} is given by \eqref{eq:incident}.

\subsection{Dimer}
The dimer is defined by two spheres, in the trapping frame this would be orientated 
by $s=[0,0,1]$ however in our scattering set up this is rotated to $s=[-1,0,0]$ as 
the large sphere is furthest from the trapping beam. We scale the position of each 
sphere by the factor L:
\begin{align}
	L = \frac{1}{k} = \frac{\lambda}{2\pi}
\end{align}

Where $\lambda$ is the wavelength of light and is given in nanometres, this means 
every position must be also provided in nanometres.

\subsection{Detectors and Pixels}
Each detector is placed roughly $2\times 10^5 nm$ from the dimer (can be adjusted 
later for testing), with the position of the detector being defined by the polar 
and azimuth angles ($\theta$ \& $\phi$ respectively) such that:
\begin{align}
	[x_{fiber}, y_{fiber}, z_{fiber}] = [rcos(\phi)sin(\theta), rsin(\phi)sin(\theta), rcos(\theta)]
\end{align}
So if you were to place the fibres in the trapping frames x-y plane (i.e. flat against
the cover slip in a covenantal trapping context), in the probe beam frame will only 
have x and z components. The orientation of the detector is just the -ve of its 
position and not scaled by the distance term r, the orientation being the vector from 
the origin of the detector to the center of the dimer.

Pixels can be thought of as points lying on the surface of the detector, by getting 
the spherical coordinates of each pixel we can compute the intensity at each point on 
the detector, allowing us to determine the average intensity on a given detector.

Where each point is first scaled to the size of the detector - for now we assume a 
radius of $2.5 \times 10^4 \ nm$ - and then translated from its position on the 
surface of the detector to the main coordinate system. Their orientation is treated 
much in the same as the detector's orientation, being its -ve position and scaled down 
by the radial distance from the dimer to the pixel, making it a unit vector. From 
their position we can also grab their spherical coordinates to create a list of points 
for mstm to evaluate. In order to accurately describe any detector surface we can use a Householder transformation to get the perpendicular circular surface of any vector.

This allows us to define the surface of any detector perpendicular to the origin of 
our coordinate system, we can freely choose the size and resolution of our fibre's. 
For every pixel we define the spherical coordinates relative to our origin, this is 
added to a list of $\theta, \phi$ pairs that are evaluated by \textit{mstm}.

>>>>

\section{Monitoring Stochastic rotational motion using static 
		light scattering}
Part of the optical fibre arrangement borrows code from the 
optical tweezer simulations discussed in Chapter 2 and 4. 
Rather than repeat the simulation details we will instead 
only focus on the specifics of the optical fibre scattering.

\subsection{Coordinate System}
Consider a particle (either a sphere or dimer) trapped by
a Gaussian beam, with its focal point being set at [0,0,0]. 
At the same time an optical fibre directs a plane wave that 
is incident on the trapped particle scattering light in all 
directions. The probe beam is assumed to be x-polarised and 
propagating in the +z direction, this is a $90^{\circ}$ 
rotation from the previous simulations (see fig\emph{X.X}).

\subsection{Dimer}
The dimer is defined by two spheres with refractive indices
of 1.59 and suspended in water ($n_{med} = 1.33$). \textit{MSTM}
requires a target origin for setting the scattering expansion, as
with our simulations we set it as the dimer's centre of diffusion.
The near field scattering from the dimer is shown in 
fig.~\ref{fig:nf_scattering}.

\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{nf_scattering_dimer.png}
	\caption{Re ${\bf E_z}$ distribution from a symmetric dimer when 
	irradiated by the probe beam (viewed in the x-y plane). Axis are 
	given in dimensionless units of $k\hat{x}$ and $k\hat{y}$ respectively.}
	\label{fig:nf_scattering}
\end{figure}

\subsection{Detectors and Pixels}
Each detector is placed some distance $\bf r$ from the origin, 
detector positions are defined by angles $\theta$ \& $\phi$. With 
$\theta=\phi=0$ being directly in front of the probe beam. The 
position of each detector is given by:
\begin{align}
	[x_{fiber}, y_{fiber}, z_{fiber}] = [rcos(\phi)sin(\theta), rsin(\phi)sin(\theta), rcos(\theta)]
\end{align}
Where r is the distance between the detector and the target origin. 
In an ideal situation the surface of the detector is oriented towards 
the target origin perfectly. Pixels can be thought of as points lying 
on the surface of the detector, each point has its own position in real
space. Using \textit{mstm} we can find the components of the scattering 
matrix at each point and compute the intensity of the electric field via:

\begin{align}
	\begin{pmatrix}
		I_s \\ Q_s \\ U_s \\ V_s
	\end{pmatrix} = 
	\begin{pmatrix}
		S_{11} & S_{12} & S_{13} & S_{14} \\
		S_{21} & S_{22} & S_{23} & S_{24} \\
		S_{31} & S_{32} & S_{33} & S_{34} \\
		S_{41} & S_{42} & S_{43} & S_{44} \\
	\end{pmatrix}
	\begin{pmatrix}
		I_i \\ Q_i \\ U_i \\ V_i
	\end{pmatrix}
\end{align}
Where:
\begin{align}
	I_s &= E_{x,\ scat}^2+E_{y,\ scat}^2 \\
	\rightarrow I_s &= S_{11}I_i+S_{12}Q_i+S_{13}U_i+S_{14}V_i
\end{align}

By computing the scattering at each point on the detectors surface 
we can compute the average scattering over the detector. As the 
detectors are moved further away from the target origin the intensity 
distribution across the detector surface falls off until near uniform.

By moving the detectors further back we can treat each detector as single
point and compute the intensity at the centre of the detector rather than
consider the full surface.
